A thesis draft

### 2018-11-19 res/sections/08-Background.tex

\section{Network slicing}
A network slice can be defined as a logical virtual network, tailored for a
given use case, on the top a common network using technologies such as
Software-Defined Networking and Network Function Chaining that allows network
softwarization~\cite{ordonez2017network}. The notion of separated virtual
networks deployed on the same infrastructure is not new, e.g. VPN, but it has
some specifics that make it a novel idea. The concept of network slicing was
first introduced in 2002 with the paper~\cite{peterson2003blueprint}, in which
is described an overlay network that allow services to access different slices
of overlay's resources and in which overlay management services run in their
own slice. This idea was be refined during time and
in~\cite{alliance2016description} the design of network slicing is based on a
three-layers model, as depicted in
Figure~\ref{chap:background:img:network_slicing}.

>>>>

\section{Network slicing}
A network slice can be defined as a logical virtual network, tailored for a
given use case, on the top a common network using technologies such as
Software-Defined Networking and Network Function Chaining that allows network
softwarization~\cite{ordonez2017network}. The notion of separated virtual
networks deployed on the same infrastructure is not new, e.g. VPN, but it has
some specifics that make it a novel idea. The concept of network slicing was
first introduced in 2002 in\cite{peterson2003blueprint}, where a network 
overlay that allows services to run continuously and to access the overlay
resources across different slices was illustrated.
Services operating over the overlay management have their own slice instead.
This idea was lately refined in 2016, where the design of network slicing was
based on a three-layers model~\cite{alliance2016description}, as depicted in 
Figure~\ref{chap:background:img:network_slicing}.
